---
title: "Assignment Five for Lab5"
author: "Taehoon Ha"
date: "10/12/2018"
output: 
    github_document:
        toc: true
        toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1.
Modify your function from the Problem 2 (Lab5 Activity). The function should simulate N rounds of the game (instead of just one) and return the proportion of times you win the bet. Run the function with $N=1,000$ and $N=10,000$.

```{r}
gambling <- function(N){
    vec <- c()
    for (i in 1:N) {
        bet <- replicate(4, sample(1:6, 1, replace = T))
        result <- sum(bet == 4) >= 1
        vec[i] <- ifelse(result, 1, 0)
    }
    return(sum(vec) / N)
}

gambling(N = 1000)
gambling(N = 10000)
```

### Question 2.
Write a function that will find the smallest element of a given vector (built-in **`min()`** is not allowed). Your function should return the smallest element and index of the smallest element.

Ex. vector is (1, 4, 2, 0, 5), then the smallest element - 0 and index is 4.

```{r}
find.min <- function(vec) {
    min.element <- vec[1]
    for (i in (seq_along(vec[-1]) + 1)) {
        if(vec[i] < min.element)
            min.element <- vec[i]
    }
    min.element
}

vec <- c(1, 4, 2, 0, 5)
find.min(vec)
```






